Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-13 doc/main_jfm.tex
removed merge conflict command
fixing merge issues

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}

@@

\section{\label{intro}Introduction}

\section{Governing  Equations}
\subsection{\label{mobility}Mobility Problem}
We consider a suspension of $N_b$ particles suspended in a
two-dimensional unbounded domain. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, ds = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, ds = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor). The
process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
\label{SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $f_i$ is a material label with $f_i = 0$ ($1$) representing
hydrophilic (hydrophobic) portions of the surface, and $\rho$ is the
decay length of attraction. The forces and torques for this attraction
are 
\begin{align}
  \label{eqn:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) dS,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

@@

\subsection{HAP Boundary Integral Equation}
Similar to our previous work~\cite{Fu20}, we represent the HAP as a
double-layer potential
\begin{align}
  \label{eqn:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, ds_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind. By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{align}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, ds_\yy,
    \quad \xx \in \bd\Omega,
\end{align}
the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
screened Laplace equation~\eqref{SL}--\eqref{SLff}. To calculate the
hydrophobic force and torque, the gradient of the double-layer
potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
particle. In Appendix~\ref{sec:appendixA}, we show that the force and
torque calculations can be expressed in terms of integral that are
non-singular.

\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we represent the velocity as
the sum of a double-layer potential and the $N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eqn:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF_i$ while the Rotlet force-free and has
torque $T_i$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eqn:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \bd \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eqn:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, ds &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eqn:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu ds &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

@@

\subsection{Self-Assembly and Relaxtion}

@@

\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}

@@

The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the friction force and the slip velocity. This quantity is given by 
\begin{equation}
b = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS},
\end{equation}
%
where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the particle pair and the centroid of the Janus-vesicle. Hence, the mean rotational velocity 
of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
For the friction force $F_f$, we calculate tangential stresses near the bilayer from outer and inner fluid then 
extrapolate the force value onto the midplane to acquire the pressure jump. The friction force is computed after integrating the pressure jump over the midplane $\Sigma_M$.
Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
within the same order, the friction coefficients are independent of the shear rates.

@@

\todo[inline]{Make figure of the paths of the two centroids....}

@@

\section{Appendices}
\label{sec:appendixA}
The stress ${\bf T}$ contains the gradient of the double layer
potential. This introduces an inherent difficulty in evaluating stress
on the boundary.  To overcome the difficulty of evaluation on
$\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular
parts:
\begin{equation}
u = u_p + v_p
\end{equation}
where  
\begin{equation}
u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nnu} \eta(y) \,\dif S(y).
\end{equation}
It turns out that the contribution to the force and torque coming from the singular
part vanishes. In particular, we will prove the identity
\begin{equation}
\label{eq:recipforcetorque}
F_p + iG_p= \int_{\Sigma_p} \gamma ({\bf I}+i{\bf X})J_{p} \,\dif S
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
J_{p} = 2\rho^{-1} \eta  v_p \nnu 
+ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nnu -  \nabla
   v_p \cdot \nnu \tau_i).
\end{equation}
Here $\nnu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
\[X_{ij} = \varepsilon_{ikj}x_k,\quad {\bf X}v = x\times v\]
where $\boldsymbol{\varepsilon}$ is the third-order alternating tensor.
We employ the Einstein summation convention and use complex vectors to streamline the presentation, $i^2 = -1$.

The benefit of using \eqref{eq:recipforcetorque} is that the integrand  is nonsingular.
The density function $\eta$ has the same smoothness as the boundary data
and $v_p$ is real-analytic in a neighborhood of $\Sigma_p$.

To prove \eqref{eq:recipforcetorque}, write
\begin{align*}
  {\bf T}
  &=
  \sigma[u_p,u_p]
  +(\sigma[u_p,v_p]
  +\sigma[v_p,u_p])
  +\sigma[v_p,v_p] \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where
\[
\sigma[u,v]
= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \otimes \nabla v.
\]
\begin{lemma}
  \label{eq:stress_div_lemma}
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
  \end{equation}
\end{lemma}
\begin{proof}
  Observe that
  \begin{align*}
    (\nabla \cdot {\bf T})_j &=
    \nabla_k   T_{jk} \\
    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
    - 2 \nabla_j u \nabla_{kk}^2 u )\\
    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u .
  \end{align*}
  Since $-\rho^2 \Delta u + u = 0$, we have $\nabla \cdot {\bf T} = 0$.
  Furthermore,
  \begin{align*}
    (\nabla \cdot (x\times {\bf T} ))_j
    &= (\nabla \cdot ({\bf X} {\bf T} ))_j
    = \nabla_k (X_{jl} T_{lk})
    = \nabla_k (\epsilon_{jml}x_m T_{lk})\\
    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
  \end{align*}
  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
  $\nabla \cdot (x \times {\bf T}) = 0$ as well.

>>>>

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}

@@

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering. Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions. 
Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu2020_SIAM}. Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle). Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent. The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019_SciRep}. Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).

In this work we extend the hybrid continuum model in \cite{Fu2020_SIAM} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow. We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions. Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we present the formulation for the Janus particles in a viscous fluid in the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus suspension to include the effects of a far-field flow via the mobility problem formulation. In \S~\ref{validation} we present validation of our model, and in \S~\ref{results} we present simulation results for a vesicle of Janus bilayer membrane under various flowing conditions. Finally we provide discussion and outlook for future directions in \S~\ref{conclusion}.~

\section{Governing  Equations}
\subsection{\label{mobility}Mobility Problem}
We consider a suspension of $N_b$ particles suspended in a
two-dimensional unbounded domain. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor). The
process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
\label{SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $f_i$ is a material label with $f_i = 0$ ($1$) representing
hydrophilic (hydrophobic) portions of the surface, and $\rho$ is the
decay length of attraction. The forces and torques for this attraction
are 
\begin{align}
  \label{eqn:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

@@

\subsection{HAP Boundary Integral Equation}
Similar to our previous work~\cite{Fu20}, we represent the HAP as a
double-layer potential
\begin{align}
  \label{eqn:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind. By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{align}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{align}
the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
screened Laplace equation~\eqref{SL}--\eqref{SLff}. To calculate the
hydrophobic force and torque, the gradient of the double-layer
potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
particle. In Section~\ref{subsec:calculating_force}, we show that the force and
torque calculations can be expressed in terms of integral that are
non-singular.

\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we represent the velocity as
the sum of a double-layer potential and the $N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eqn:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF_i$ while the Rotlet force-free and has
torque $T_i$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eqn:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \bd \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eqn:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eqn:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

\subsection{Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
The stress \eqref{eq:stress} contains
contains the gradient of the double-layer potential \eqref{eqn:HAP_DLP},
making it difficult to evaluate
the forces and torques \eqref{eqn:hydrophobicAttraction}.
The identities \eqref{eq:recipforcetorque}
make it possible to evaluate the forces and torques
without specialized quadrature methods.

Consider the particle
$\Gamma_i$ indexed by $i$
and decompose $u$ as follows: 
\begin{equation}
u = u_i + v_i
\end{equation}
where  
\begin{equation}
    u_i(\xx) = \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega.
\end{equation}
That is, $u_i$ is the double-layer potential for the restriction of $\sigma$ to $\Gamma_i$.  Let $\FF_i$ and $T_i$ be as in \eqref{eqn:hydrophobicAttraction}. We prove that 
\begin{equation}
\label{eq:recipforcetorque}
\FF_i= \int_{\Gamma_i} \JJ_i \,\dif s,\quad
T_i= \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
\JJ_{i} = 2\gamma\left[\rho^{-1} u v_i \nnu 
+ \rho \nabla u \cdot \tau (\nabla v_i \cdot \tau \nnu -  \nabla
   v_i \cdot \nnu \tau)\right].
\end{equation}
Here $\nnu$ is the unit normal and $\tau$ is a unit tangent vector.
Observe that  $u$ and $\nabla u \cdot \tau$ come from the boundary data $f_i$ \eqref{SLbc} and are smooth. The functions $v_i$ and $\nabla v_i$
come from double-layer integrals that are smooth on $\Gamma_i$.

To prove \eqref{eq:recipforcetorque},
let \begin{align*}
  {\bf T}
  &=
  \sigma[u_i,u_i]
  +(\sigma[u_i,v_i]
  +\sigma[v_i,u_i])
  +\sigma[v_i,v_i] \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we have introduced the notation
\[
\sigma[u,v]
= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \nabla v^T.
\]
Using the fact that $u$, $u_i$, and $v_i$ solve the equation
$-\rho^2 \Delta u + u = 0$, and that ${\bf T}$ is symmetric,
it is straightforward to show that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
  \end{equation}

\begin{lemma}
  \label{eq:stress_div_lemma}
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
  \end{equation}
\end{lemma}
\begin{proof}
  The function $u$ solves $-\rho^2 \Delta u + u = 0$. Using the summation convention, 
  \begin{align*}
    (\nabla \cdot {\bf T})_j &=
    \nabla_k   T_{jk} \\
    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
    - 2 \nabla_j u \nabla_{kk}^2 u )\\
    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u = 0.
  \end{align*}
Moreover, 
  \begin{align*}
    (\nabla \cdot (\xx \times {\bf T} ))_j
    &= \nabla_k (\epsilon_{jml}x_m T_{lk})\\
    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
  \end{align*}
  where $\varepsilon_{jml}$ is the alternating tensor. 
  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
  $\nabla \cdot (x \times {\bf T}) = 0$ as well.

@@

\subsection{Self-Assembly and Relaxation}

@@

%\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}

@@

The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the friction force and the slip velocity. This quantity is given by 
\begin{equation}
b = \frac{F_f}{\int_{\Sigma_M} R \dot\theta \dif s},
\end{equation}
%
where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the particle pair and the centroid of the Janus-vesicle. Hence, the mean rotational velocity 
of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
For the friction force $F_f$, we calculate tangential stresses near the bilayer from outer and inner fluid then 
extrapolate the force value onto the midplane to acquire the pressure jump. The friction force is computed after integrating the pressure jump over the midplane $\Sigma_M$.
Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
within the same order, the friction coefficients are independent of the shear rates.

@@

%\todo[inline]{Make figure of the paths of the two centroids....}

@@

\section{Appendices}
\label{sec:appendixA}
